---
title: "National Data"
author: "Data is from 2011-2015 ACS 5-Year File"
output: 
  html_document:
    theme: yeti
    css: style.css
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
national_cvap<- readxl::read_xlsx("national_dta.xlsx", sheet = "CVAP")
national_edu<- readxl::read_xlsx("national_dta.xlsx", sheet = "Education")
national_edu<- national_edu %>% rename(`HS/GED` = total_hsged,
                                       `HS or Higher` = total_hs_higher,
                                       `Bachelor's` = total_ba,
                                       `BA or Higher` = total_ba_higher)


```

Use the Table of Contents to Select the topic, then use the tabs to select the population group



## Citizen Voting Age Population {.tabset .tabset-fade .tabset-pills}



### Major Racial Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_cvap %>%
  filter(group_ID ==  "Major Racial Groups") %>%
  arrange(desc(CVAP)) %>%
  rename(Total = total_pop)%>%
  select(Group, CVAP,Total )%>%
  datatable(extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
```


### Asian Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_cvap %>%
  filter(group_ID ==  "Asian Detail") %>%
  arrange(desc(CVAP)) %>%
  rename(Total = total_pop)%>%
  select(Group, CVAP,Total)%>%
    datatable(colnames = c('Group-Alone' = 'Group'), extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
```

### Asian Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_cvap %>%
  filter(group_ID ==  "Asian Detail Combo") %>%
  arrange(desc(CVAP)) %>%
  rename(Total = total_pop)%>%
  select(Group, CVAP,Total)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brtp',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
```

### NHPI Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_cvap %>%
  filter(group_ID ==  "NHPI Detail") %>%
  arrange(desc(CVAP)) %>%
  rename(Total = total_pop)%>%
  select(Group, CVAP,Total)%>%
   datatable(colnames = c('Group-Alone' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
```

### NHPI Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_cvap %>%
  filter(group_ID ==  "NHPI Detail Combo") %>%
  arrange(desc(CVAP)) %>%
  rename(Total = total_pop)%>%
  select(Group, CVAP,Total)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
```


## Education {.tabset .tabset-fade .tabset-pills}

### Major Racial Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Major Racial Groups") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
  datatable(extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```


### Asian Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Asian Detail") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
  datatable(colnames = c('Group-Alone' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

### Asian Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Asian Detail Combo") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

### NHPI Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "NHPI Detail") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

### NHPI Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "NHPI Detail Combo") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

