---
title: ""
author: ""
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)

# Setting Number formatting 
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)

# Read in data from excel file
national_cvap<- readxl::read_xlsx("national_dta.xlsx", sheet = "CVAP")
national_edu<- readxl::read_xlsx("national_dta.xlsx", sheet = "Education")


# Renaming columns we could probably kill this code later to streamline
national_edu<- national_edu %>% rename(`HS/GED` = total_hsged,
                                       `HS or Higher` = total_hs_higher,
                                       `Bachelor's` = total_ba,
                                       `BA or Higher` = total_ba_higher)


### Creating functions to cut down on repeat code
national_cvap_display <- function(data,group){
  data %>%
    filter(group_ID ==  paste(group)) %>%
    arrange(desc(CVAP)) %>%
    rename(Total = total_pop)%>%
    select(Group, CVAP,Total )%>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2,3),currency = "", interval = 3, mark = ",", digits=0)
}

```

<div class="jumbotron">
  <h1>National Data</h1>
  <p>Use the buttons to select the topic and then the tabs for population groups</p>
</div>



# Citizen Voting Age Population {.tabset .tabset-fade .tabset-pills}

> Citizen Voting Age Population (CVAP) data is complied using Table [B05003](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05003) from the 2015 ACS 5-Year estimates.

## Major Racial Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}

national_cvap_display(national_cvap,"Major Racial Groups")

```


## Asian Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}

national_cvap_display(national_cvap,"Asian Detail")


```

## Asian Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}

national_cvap_display(national_cvap,"Asian Detail Combo")


```

## NHPI Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}

national_cvap_display(national_cvap,"NHPI Detail")

```

## NHPI Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}


national_cvap_display(national_cvap,"NHPI Detail Combo")

```


# Education {.tabset .tabset-fade .tabset-pills}

## Major Racial Groups
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Major Racial Groups") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID) %>%
  mutate(BA_Higher = round((`BA or Higher`/Total)*100,2))%>%
hchart( "bar", hcaes(x = Group, y = BA_Higher)) %>%
hc_add_theme(hc_theme_tufte()) %>% # hc_colors("#008fd5") %>%
  hc_yAxis(title = list(text = "Bachelor's Degree or Higher"),
         labels= list(style =list(color ="black", fontSize='12px'),
                      format= "{value}%"), max = 100, opposite=TRUE) %>%
  hc_xAxis(title = list(text = ""),
           labels= list(style =list(color ="#E26069", fontSize='15px')),
            minorTickLength= 0,tickLength=0) %>%
   hc_tooltip(pointFormat = "{point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069"))

national_edu %>%
  filter(group_ID ==  "Major Racial Groups") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
  datatable(extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```


## Asian Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Asian Detail") %>%
  rename(Total = total_pop)%>%
  select(-group_ID) %>%
  mutate(BA_Higher = round((`BA or Higher`/Total)*100,2))%>%
  arrange(desc(BA_Higher)) %>%
hchart( "bar", hcaes(x = Group, y = BA_Higher)) %>%
hc_add_theme(hc_theme_tufte()) %>%
  hc_yAxis(title = list(text = "Bachelor's Degree or Higher"),
         labels= list(style =list(color ="black", fontSize='12px'),
                      format= "{value}%"), max = 100,opposite=TRUE) %>%
  hc_xAxis(title = list(text = "Group"),
           labels= list(style =list(color ="#E26069", fontSize='15px'))) %>%
   hc_tooltip(pointFormat = "{point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069"))

national_edu %>%
  filter(group_ID ==  "Asian Detail") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
  datatable(colnames = c('Group-Alone' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

## Asian Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "Asian Detail Combo") %>%
  rename(Total = total_pop)%>%
  select(-group_ID) %>%
  mutate(BA_Higher = round((`BA or Higher`/Total)*100,2))%>%
  arrange(desc(BA_Higher)) %>%
hchart( "bar", hcaes(x = Group, y = BA_Higher)) %>%
hc_add_theme(hc_theme_tufte()) %>%
  hc_yAxis(title = list(text = "Bachelor's Degree or Higher"),
         labels= list(style =list(color ="black", fontSize='12px'),
                      format= "{value}%"), max = 100,opposite=TRUE) %>%
  hc_xAxis(title = list(text = "Group"),
           labels= list(style =list(color ="#E26069", fontSize='12px'))) %>%
   hc_tooltip(pointFormat = "{point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069"))

national_edu %>%
  filter(group_ID ==  "Asian Detail Combo") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

## NHPI Detailed Origin
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "NHPI Detail") %>%
  rename(Total = total_pop)%>%
  select(-group_ID) %>%
  mutate(BA_Higher = round((`BA or Higher`/Total)*100,2))%>%
  arrange(desc(BA_Higher)) %>%
hchart( "bar", hcaes(x = Group, y = BA_Higher)) %>%
hc_add_theme(hc_theme_tufte()) %>%
  hc_yAxis(title = list(text = "Bachelor's Degree or Higher"),
         labels= list(style =list(color ="black", fontSize='12px'),
                      format= "{value}%"), max = 100,opposite=TRUE) %>%
  hc_xAxis(title = list(text = "Group"),
           labels= list(style =list(color ="#E26069", fontSize='15px'))) %>%
   hc_tooltip(pointFormat = "{point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069"))
national_edu %>%
  filter(group_ID ==  "NHPI Detail") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

## NHPI Detailed Origin Combo
```{r echo=FALSE, message=FALSE, warning=FALSE}
national_edu %>%
  filter(group_ID ==  "NHPI Detail Combo") %>%
  rename(Total = total_pop)%>%
  select(-group_ID) %>%
  mutate(BA_Higher = round((`BA or Higher`/Total)*100,2))%>%
  arrange(desc(BA_Higher)) %>%
hchart( "bar", hcaes(x = Group, y = BA_Higher)) %>%
hc_add_theme(hc_theme_tufte()) %>%
  hc_yAxis(title = list(text = "Bachelor's Degree or Higher"),
         labels= list(style =list(color ="black", fontSize='12px'),
                      format= "{value}%"), max = 100,opposite=TRUE) %>%
  hc_xAxis(title = list(text = "Group"),
           labels= list(style =list(color ="#E26069", fontSize='15px'))) %>%
   hc_tooltip(pointFormat = "{point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069"))
national_edu %>%
  filter(group_ID ==  "NHPI Detail Combo") %>%
  arrange(desc(total_pop)) %>%
  rename(Total = total_pop)%>%
  select(-group_ID)%>%
   datatable(colnames = c('Group-Alone/Combo' = 'Group'),extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatCurrency(columns = c(2:6),currency = "", interval = 3, mark = ",", digits=0)
```

