---
title: ""
author: ""
output: 
  html_document:
    css: style.css
    
---

```{r setup-1-general, include=FALSE}

library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)

# Setting Number formatting 
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)

# Read in data from excel file
pop_id_lookup <- read_csv("pop_id_lookup.csv")
national_cvap<- readxl::read_xlsx("national_dta.xlsx", sheet = "cvap")
national_edu<- readxl::read_xlsx("national_dta.xlsx", sheet = "edu")
national_lep<- readxl::read_xlsx("national_dta.xlsx", sheet = "lep")

national_edu<-national_edu %>% left_join(pop_id_lookup) %>% select(-geoid, - geodisplaylabel)
national_lep<-national_lep %>% left_join(pop_id_lookup) %>% select(-geoid, - geodisplaylabel)

## Column Groups?
cvap_columns <- c("Group", "CVAP", "Total")
education_columns <- c("Group", "Total","Less than HS", "HS or GED", "Some College or AA", "BA or higher")
lep_columns <- c("Group", "Total Pop", "Speak Other Language","LEP", "Total LEP")

national_cvap <-national_cvap %>% rename(Total = total_pop)

national_tbl_display <- function(data,group,column_names,orderby){
  data %>%
    filter(group_id ==  paste(group)) %>%
    select(column_names) %>%
    #arrange(desc(paste(orderby)))%>%
    datatable(extensions = 
                list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
              rownames= FALSE, 
              options = list(
                dom = 'rtB',
                buttons = c('copy', 'csv', 'excel'),
                scrollX = TRUE,
                lengthMenu = c(25, 50, 100), pageLength = 50))
}


```

```{r setup-1-education, include=FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty
national_edu <- national_edu %>% 
  mutate(est_hsless = 
            case_when( check_hsless == 1 ~  NA_real_ ,TRUE ~ est_hsless),
         est_hsged  =
          case_when( check_hsged == 1 ~  NA_real_ ,TRUE ~ est_hsged),
         est_somecollegeaa  =
          case_when( check_somecollegeaa == 1 ~  NA_real_ ,TRUE ~ est_somecollegeaa),
         est_bahigher  =
          case_when( check_bahigher == 1 ~  NA_real_ ,TRUE ~ est_bahigher))
      
national_edu <- national_edu %>% select(-check_hsless,
                                  -check_hsged,
                                  -check_somecollegeaa,
                                  -check_bahigher)

national_edu <- national_edu %>% mutate(
  pct_hsless   = est_hsless/est_totpop,
  pct_bahigher = est_bahigher/ est_totpop)

national_edu<- national_edu %>% rename(Total = est_totpop,
         `Less than HS` = est_hsless,
         `HS or GED` = est_hsged,
         `Some College or AA` = est_somecollegeaa,
         `BA or higher` = est_bahigher,
         Group = group_name)




```

```{r setup-1-lep, include=FALSE}

### Getting Rid of Estimates where the "CHECK" variable is flagging uncertainty

national_lep <- national_lep %>% 
  mutate(pct_lep = 
            case_when( checking_lep == 1 ~  NA_real_ ,TRUE ~ pct_lep),
         est_lep = 
            case_when( checking_lep == 1 ~  NA_real_ ,TRUE ~ est_lep),
         est_other_lang = 
            case_when( checking_other_lang == 1 ~  NA_real_ ,TRUE ~ est_other_lang),
         est_totalpop = 
            case_when( checking_totpop == 1 ~  NA_real_ ,TRUE ~ est_totalpop))

national_lep <- national_lep %>% 
  mutate(pct_other_lang = est_other_lang/est_totalpop)  

national_lep<- national_lep %>% rename(Group = group_name,
                                       `LEP` = pct_lep,
                                       `Total LEP` = est_lep,
                                       `Total Pop` = est_totalpop,
                                       `Total Speak Other Language` = est_other_lang,
                                       `Speak Other Language` = pct_other_lang)

```

<div class="jumbotron">
  <h1>National Data</h1>
  <p>Use the buttons to select the topic and then the tabs for population groups</p>
</div>



# Citizen Voting Age Population {.tabset .tabset-fade .tabset-pills}

> Citizen Voting Age Population (CVAP) data is complied using Table [B05003](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B05003) from the 2015 ACS 5-Year estimates.

## Major Racial Groups
```{r cvap major groups, echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_cvap,"Major racial groups",cvap_columns,"CVAP") %>% 
  formatCurrency(columns = cvap_columns,currency = "", interval = 3, mark = ",", digits=0)

```


## Asian Detailed Origin
```{r cvap asian alone, echo=FALSE, message=FALSE, warning=FALSE}


national_tbl_display(national_cvap,"Asian Detail",cvap_columns,"CVAP")%>% 
  formatCurrency(columns = cvap_columns,currency = "", interval = 3, mark = ",", digits=0)


```

## Asian Detailed Origin Combo
```{r cvap asian combo, echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_cvap,"Asian Detail Combo",cvap_columns,"CVAP")%>% 
  formatCurrency(columns = cvap_columns,currency = "", interval = 3, mark = ",", digits=0)


```

## NHPI Detailed Origin
```{r cvap nhpi alone, echo=FALSE, message=FALSE, warning=FALSE}


national_tbl_display(national_cvap,"NHPI Detail",cvap_columns,"CVAP")%>% 
  formatCurrency(columns = cvap_columns,currency = "", interval = 3, mark = ",", digits=0)

```

## NHPI Detailed Origin Combo
```{r cvap nhpi combo, echo=FALSE, message=FALSE, warning=FALSE}


national_tbl_display(national_cvap,"NHPI Detail Combo",cvap_columns,"CVAP")%>% 
  formatCurrency(columns = cvap_columns,currency = "", interval = 3, mark = ",", digits=0)

```



# Education {.tabset .tabset-fade .tabset-pills}

> Educational Attainment data is complied using Table [B15002](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B15002) from the 2015 ACS 5-Year estimates.

According to the latest national estimates, about **1 in 2** Asian Americans have a Bachelor's Degree or higher compared to about **1 in 3** Americans and **1 in 5** NHPIs.

```{r edu graph major groups, echo=FALSE, message=FALSE, warning=FALSE}



national_edu %>% 
  filter(group_id ==  "Major racial groups") %>%
  select(Group, pct_hsless, pct_bahigher) %>% 
  arrange(desc(pct_bahigher)) %>%
  mutate(`BA or Higher` = round((pct_bahigher*100),2),
         `Less than HS` = round((pct_hsless*100),2))  %>%
   select(-pct_hsless, -pct_bahigher) %>%
  gather(estimate_type,estimate, -Group) %>%
hchart( "bar", hcaes(x = Group , y = estimate, group = estimate_type)) %>%
hc_add_theme(hc_theme_tufte2()) %>%  hc_colors(colors = c("#E26069","#008fd5")) %>%
  hc_yAxis(title = list(text = ""),
         labels= list(style =list(color ="black", fontSize='18px'),
                      format= "{value}%"), max = 100, opposite=TRUE) %>%
  hc_xAxis(title = list(text = ""),
           labels= list(style =list(color ="#E5790D", fontSize='20px')),
            minorTickLength= 0,tickLength=0) %>%
   hc_tooltip(pointFormat = "{series.name}: {point.y}%") %>%
 hc_title(text = "Educational Attainment",
           margin = 20, align = "left",
           style = list(color = "#E5790D"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E5790D"))
```


## Major Racial Groups
```{r edu major groups, echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_edu,"Major racial groups",education_columns,"Total")%>% 
  formatCurrency(columns = education_columns,currency = "", interval = 3, mark = ",", digits=0)

```


## Asian Detailed Origin
```{r edu asian alone, echo=FALSE, message=FALSE, warning=FALSE}
national_tbl_display(national_edu,"Asian Detail",education_columns,"Total")%>% 
  formatCurrency(columns = education_columns,currency = "", interval = 3, mark = ",", digits=0)

```

## Asian Detailed Origin Combo
```{r edu asian combo, echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_edu,"Asian Detail Combo",education_columns,"Total")%>% 
  formatCurrency(columns = education_columns,currency = "", interval = 3, mark = ",", digits=0)


```

## NHPI Detailed Origin
```{r edu nhpi alone, echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_edu,"NHPI Detail",education_columns,"Total")%>% 
  formatCurrency(columns = education_columns,currency = "", interval = 3, mark = ",", digits=0)



```

## NHPI Detailed Origin Combo
```{r edu nhpi combo,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_edu,"NHPI Detail Combo",education_columns,"Total")%>% 
  formatCurrency(columns = education_columns,currency = "", interval = 3, mark = ",", digits=0)


```



# Limited English Proficiency {.tabset .tabset-fade .tabset-pills}

> Limited English Proficiency (LEP) refers to the proportion of individuals who a language other than english at home & speak english less than "very well".
Limited English Proficiency data is complied using Table [B16004](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/15_5YR/B16004) from the 2015 ACS 5-Year estimates.


```{r lep_graph, echo=FALSE, message=FALSE, warning=FALSE}
national_lep %>%
  filter(group_id ==  "Major racial groups") %>%
  select(lep_columns) %>% 
  mutate(pct_other = round(`Speak Other Language`*100,2),
                                 pct_lep = round(LEP *100,2)) %>%
  arrange(desc(pct_other)) %>% hchart( "bar", hcaes(x = Group , y = pct_other)) %>%
  hc_add_theme(hc_theme_tufte2()) %>%  hc_colors(colors = c("#008fd5")) %>%
  hc_yAxis(title = list(text = ""),
         labels= list(style =list(color ="black", fontSize='15px'),
                      format= "{value}%"), max = 100, opposite=TRUE) %>%
  hc_xAxis(title = list(text = ""),
           labels= list(style =list(color ="#E5790D", fontSize='15px')),
            minorTickLength= 0,tickLength=0) %>%
  hc_tooltip(useHTML=T,pointFormat = "About <span style = 'color:#E26069'>{point.y:.0f}%</span> speak a language other than english at home <br> and of those, <span style = 'color:#E26069'>{point.pct_lep:.0f}%</span> are LEP.") %>%
   hc_title(text = "Speak a language other than english",
           margin = 20, align = "left",
           style = list(color = "#E5790D"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E5790D"))

```



## Major racial groups
```{r lep major groups,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_lep,"Major racial groups",lep_columns,"Total Lep")%>% 
  formatPercentage(columns = c("LEP","Speak Other Language"), digits = 2) %>% 
  formatCurrency(columns = c("Total LEP", "Total Pop"),currency = "", interval = 3, mark = ",", digits=0)

```


## Asian Detailed Origin
```{r lep asian detail,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_lep,"Asian Detail",lep_columns,"Total Lep")%>% 
  formatPercentage(columns = c("LEP","Speak Other Language"), digits = 2) %>% 
  formatCurrency(columns = c("Total LEP", "Speak Other Language", "Total Pop"),currency = "", interval = 3, mark = ",", digits=0)
```


## Asian Detailed Origin Combo
```{r lep asn combo,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_lep,"Asian Detail Combo",lep_columns,"Total Lep")%>% 
  formatPercentage(columns =c("LEP","Speak Other Language"), digits = 2) %>% 
  formatCurrency(columns = c("Total LEP", "Speak Other Language", "Total Pop"),currency = "", interval = 3, mark = ",", digits=0)

```

## NHPI Detailed Origin
```{r lep nhpi detail,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_lep,"NHPI Detail",lep_columns,"Total Lep")%>% 
  formatPercentage(columns = c("LEP","Speak Other Language"), digits = 2) %>% 
  formatCurrency(columns = c("Total LEP", "Speak Other Language", "Total Pop"),currency = "", interval = 3, mark = ",", digits=0)

```


## NHPI Detailed Origin Combo
```{r lep nhpi combo,echo=FALSE, message=FALSE, warning=FALSE}

national_tbl_display(national_lep,"NHPI Detail Combo",lep_columns,"Total Lep")%>% 
  formatPercentage(columns = c("LEP","Speak Other Language"), digits = 2) %>% 
  formatCurrency(columns = c("Total LEP", "Speak Other Language", "Total Pop"),currency = "", interval = 3, mark = ",", digits=0)

```
