---
title: ""
author: ""
output: 
  html_document:
    toc: true
    toc_float: true
    css: style.css
---

```{r setup, include=FALSE}
library(forcats)
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)
library(glue)
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)
#national_cvap<- readxl::read_xlsx("state_dta.xlsx", sheet = "CVAP")
state_edu<- readxl::read_xlsx("state_dta.xlsx")
state_edu$pop_id<- as.factor(state_edu$pop_id) 
state_edu <- state_edu %>% mutate(
  pct_hs_higher = tot_hs_higher/total,
  pct_ba_higher = tot_bahigher/total)

state_edu_long<- state_edu %>% select(-pop_group , -tot_hs_higher,-tot_bahigher )  %>%
  gather(estimate_type, estimate, -Geography ,-pop_id) %>% filter(estimate_type !="total")

#state_edu<- state_edu %>% rename( `HS or Higher` = tot_hs_higher,
#                                       `BA or Higher` = tot_bahigher)

avg_hs_higher <- state_edu %>% filter(pop_id == 1) %>% select(Geography, pct_hs_higher) %>%  summarize(mean = mean(pct_hs_higher)) %>% pull() %>% round(.,4)
avg_hs_higher <- avg_hs_higher*100

## Pulling National BA or Higher Percentage
avg_ba_higher <- state_edu %>% filter(pop_id == 1) %>% select(Geography, pct_ba_higher) %>%  summarize(mean = mean(pct_ba_higher)) %>% pull() %>% round(.,4)
avg_ba_higher <- avg_ba_higher*100

racial_groups<- c(1,2,4,6,12,32,50,60)
aapi_alone<- c(1,12,50)
aapi_combo<- c(1,31,60)

Asian_orign_alone <- c(13:29)
Asian_origin_combo<- c(32:48)
NHPI_origin_alone <- c(51,55,56)
NHPI_origin_combo<- c(61:66)

state_edu_alone <- state_edu_long  %>% filter(pop_id %in% aapi_alone )
state_edu_alone$pop_id <- fct_recode(state_edu_alone$pop_id,
               "State Population" = "1",
               "Asian" = "12",
               "NHPI" = "50")
## Recoding state_edu_alone$estimate_type
state_edu_alone$estimate_type <- fct_recode(state_edu_alone$estimate_type,
               "HS or Higher" = "pct_hs_higher",
               "BA or Higher" = "pct_ba_higher",
               "Total" ="total")

state_edu_combo <- state_edu_long  %>% filter(pop_id %in% aapi_combo )
state_edu_combo$pop_id <- fct_recode(state_edu_combo$pop_id,
              "State Population" = "1",
               "Asian" = "31",
               "NHPI" = "60")
               
## Recoding state_edu_alone$estimate_type
state_edu_combo$estimate_type <- fct_recode(state_edu_combo$estimate_type,
               "HS or Higher" = "pct_hs_higher",
               "BA or Higher" = "pct_ba_higher",
               "Total" ="total")


# state_edu_combo_origin <- state_edu_long  %>% filter(pop_id %in% Asian_origin_combo )
# state_edu_combo_origin$pop_id <- fct_recode(state_edu_combo_origin$pop_id,
#                 "Asian Indian" = "32",
#                "Cambodian" = "34",
#                "Chinese" = "35",
#                "Chinese (except, Taiwanese)" = "36",
#                "Filipino" = "38",
#                "Japanese" = "41",
#                "Korean" = "42",
#                "Laotian" = "43",
#                "Pakistani" = "45",
#                "Thai" = "47",
#                "Vietnamese" = "48")
# ## Recoding state_edu_alone$estimate_type
# state_edu_combo_origin$estimate_type <- fct_recode(state_edu_combo_origin$estimate_type,
#                "HS or Higher" = "pct_hs_higher",
#                "BA or Higher" = "pct_ba_higher",
#                "Total" ="total")



```

<div class="jumbotron">
  <h1>State Data</h1>
  <p>Use the buttons to select the topic and then the tabs for population groups</p>
</div>

# Education {.tabset .tabset-fade .tabset-pills}
These tables use the 2011-2015 5YR data from the American Community Survey.

## Asian & NHPI Alone

Nationally, about **`r avg_hs_higher`%** of Americans have a HS degree or higher and about **`r avg_ba_higher`%** have a Bachelor's Degree or higher.
```{r echo=FALSE, message=FALSE, warning=FALSE}

state_edu_table <-state_edu_alone %>%
  mutate(long_key=paste(pop_id, estimate_type, sep=": ")) %>% #Combining Pop_ID and Estimate type
  select(-pop_id, -estimate_type) %>% 
  spread(long_key, estimate,fill = " - ") %>% 
  rename(State= Geography)
#Reordering columns

state_edu_table <- state_edu_table [c(1,6,7,2,3,4,5)]
ix <- 2:7 
state_edu_table[ix] <- lapply(state_edu_table[ix], as.numeric) 
state_edu_table %>%
 datatable(extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatPercentage(columns=c(2,3,4,5,6,7),2)

```

## Asian & NHPI Combo
Nationally, about **`r avg_hs_higher`%** of Americans have a HS degree or higher and about **`r avg_ba_higher`%** have a Bachelor's Degree or higher.

```{r echo=FALSE, message=FALSE, warning=FALSE}

state_edu_table_combo <-state_edu_combo %>%
  mutate(long_key=paste(pop_id, estimate_type, sep=": ")) %>% #Combining Pop_ID and Estimate type
  select(-pop_id, -estimate_type) %>% 
  spread(long_key, estimate,fill = " - ") %>% 
  rename(State= Geography) 
#Reordering columns
state_edu_table_combo <- state_edu_table_combo [c(1,6,7,2,3,4,5)]
ix <- 2:7 
state_edu_table_combo[ix] <- lapply(state_edu_table_combo[ix], as.numeric) 

state_edu_table_combo %>%
 datatable(extensions = 
              list("Buttons" = NULL, 'FixedColumns'= T, "Scroller"=T),
            rownames= FALSE, 
            options = list(
              dom = 'Brt',
              buttons = c('copy', 'csv', 'excel'),
              scrollX = TRUE,
              fixedColumns = list(leftColumns = 1),
              lengthMenu = c(25, 50, 100), pageLength = 50)) %>% formatPercentage(columns=c(2,3,4,5,6,7),2)

```





## Visualize Data
```{r echo=FALSE, message=FALSE, warning=FALSE}

mapdata <- get_data_from_map(download_map_data("countries/us/us-all"))
state_edu_table <- state_edu_table %>% mutate(value = `State Population: BA or Higher`*100, na.omit=T)
state_edu_table <- state_edu_table %>% mutate(value2 = `Asian: BA or Higher`*100, na.omit=T)
state_edu_table <- state_edu_table %>% mutate(value3 = `NHPI: BA or Higher`*100, na.omit=T)
library(acs)
data(fips.state)
fips.state <- fips.state %>% rename(State = STATE_NAME)
state_edu_table<- state_edu_table %>% inner_join(fips.state, by = "State")

# hcmap("countries/us/us-all",type ="tilemap", data = state_edu_table, value = "value",
#       joinBy = c("hc-a2", "STUSAB"), name = "BA or Higher",
#       dataLabels = list(enabled = TRUE, format = '{point.name}'),
#       borderColor = "#FAFAFA", borderWidth = 0.1,
#       tooltip = list(valueDecimals = 2, valueSuffix = "%")) %>%
#       hc_add_theme(hc_theme_flat()) %>%
#        hc_title(text =" State BA or Higher",
#            margin = 20, align = "left",
#            style = list(color = "#E26069"))%>%
#       hc_subtitle(text = "(2011-2015 ACS)",
#             margin = 20, align = "left",
#            style = list(color = "#E26069"))
   
data("usgeojson")


# highchart() %>%
#   hc_title(text = "Bachelors Degree or Higher", align = "center") %>%
#   hc_subtitle(text = "Source: 2011-2015 ACS", align = "center") %>%
#   hc_add_series_map(usgeojson, state_edu_table, name = "Educational Attainment",
#   value = "value", joinBy = c("postalcode", "STUSAB"),
#   tooltip = list(useHTML = TRUE,
#                  valueDecimals = 1, valueSuffix = "%",
#                  pointFormat = "{point.name}: {point.value} <br> Asian Alone {point.value2:.1f}% <br> NHPI Alone {point.value3:.1f}%",table = T)) %>%
#   hc_add_theme(hc_theme_538()) %>%
#   hc_colorAxis(stops = color_stops(),labels= list(format = "{value}%"),showInLegend=T) %>%
#    hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
#             layout = "horizontal", padding = 5) 

x <- c("{point.name}:", "Asian Alone:","NHPI Alone:")
title<-"Percent BA or Higher"
y <- c(" {point.value:.1f}%", " {point.value2:.1f}%",
" {point.value3:.1f}%")
style <- "style=font-size:80%"
#tooltip_table(x, y, title= title, style)

#testing<- "Percent BA or Higher \n <table style='font-family:'Avenir Next'; font-size:2vmin'>\n  <tr>\n  <th>{point.name}:</th>\n    <td> {point.value:.1f}%</td>\n  </tr>\n  <tr>\n    <th>Asian Alone:</th>\n    <td> #{point.value2:.1f}%</td>\n  </tr>\n  <tr>\n    <th>NHPI Alone:</th>\n    <td> {point.value3:.1f}%</td>\n  </tr>\n</table>"

highchart() %>%
  hc_title(text = "Bachelors Degree or Higher", align = "center") %>%
  hc_subtitle(text = "Source: 2011-2015 ACS using Asian/NHPI Alone", align = "center") %>%
  hc_add_series_map(usgeojson, state_edu_table, name = "Education",value = "value", joinBy = c("postalcode", "STUSAB")) %>%
  hc_tooltip(pointFormat = tooltip_table(x,y,title), useHTML=T,  headerFormat= "")%>%
  hc_add_theme(hc_theme_538()) %>%
  hc_colorAxis(stops = color_stops(),labels= list(format = "{value}%"),showInLegend=T) %>%
   hc_legend(title = list(text= "Statewide Percentage", fontStyle ='italic'),align = "center",verticalAlign = "bottom",
            layout = "horizontal", padding = 5) 




```

